First steps in synthetic algebraic geometry

### 2017-03-13 snippets/open-subfunctors.tex
Further characterization of openness

\begin{prop}\label{prop:characterization-open-subfunctor}
Let~$X \in \Zar(S)$ be a Zariski sheaf. A subfunctor~$U
\hookrightarrow X$ is open if and only if
\begin{multline*}
  \Zar(S) \models
  \forall x\?X\_
  \exists J \subseteq \affl\_ \\
  \speak{$J$ is an ideal} \wedge
  \speak{$\affl/J$ is quasicoherent} \wedge
  (x \in U \Leftrightarrow 1 \in J).
\end{multline*}
\end{prop}

The displayed condition is only meaningful in an intuitionistic
context as provided by the big Zariski topos. In classical logic, the condition
would be trivially satisfied, for any~$U$: Classically, we have~$(x \in U) \vee
(x \not\in U)$. If~$x \in U$, we can pick~$J = (1)$,
and if~$x \not\in U$, we can pick~$J = (0)$.

@@

\begin{proof}[Proof of Proposition~\ref{prop:characterization-open-subfunctor}]
\end{proof}

>>>>

\begin{prop}\label{prop:characterization-open-subfunctor}
Let~$X \in \Zar(S)$ be a Zariski sheaf. A subfunctor~$U
\hookrightarrow X$ is open if and only if any of the following conditions,
formulated in the internal language of~$\Zar(S)$, is
satisfied.
\begin{enumerate}
\item For all~$x \? X$ there is an ideal~$J \subseteq \affl$ such
that~$\affl/J$ is quasicoherent and such that~$x \in U$ if and only if~$1 \in
J$. In formal language:
\begin{multline*}
  \qquad\qquad\Zar(S) \models
  \forall x\?X\_
  \exists J \subseteq \affl\_ \\
  \speak{$J$ is an ideal} \wedge
  \speak{$\affl/J$ is quasicoherent} \wedge
  (x \in U \Leftrightarrow 1 \in J). \end{multline*}
\item For all~$x \? X$ the quotient~$\affl/K$ modulo the radical ideal
\[ K \defeq \{ f\?\affl \,|\, \speak{$f$ \inv} \Rightarrow (x \in U) \}
\subseteq \affl \]
is quasicoherent.
\end{enumerate}
\end{prop}

The displayed conditions are only meaningful in an intuitionistic context as
provided by the big Zariski topos. For instance, the first condition would be
trivially satisfied in classical logic, for any subfunctor~$U \hookrightarrow
X$: Classically, we have~$(x \in U) \vee (x \not\in U)$. If~$x \in U$, we can
pick~$J = (1)$, and if~$x \not\in U$, we can pick~$J = (0)$ (such that the
quotient~$\affl/J$ is isomorphic to~$\affl$, thus finitely presented and
therefore in particular quasicoherent).\footnote{Strictly speaking,
incompability with classical logical surfaces even earlier: in our internal
quasicoherence condition. The map~$E \otimes_\affl A \to [\Spec(A), E]$ which
the condition demands to be bijective has hardly any chance to be surjective if
the law of excluded middle is available to define maps~$\Spec(A) \to E$ by case
distinction.}

@@

\begin{proof}[Proof of Proposition~\ref{prop:characterization-open-subfunctor}]

\end{proof}
